The Astropy Project

### 2017-10-24 main.tex
affiliated packages
provisionally accepted packages
Update on Overleaf.

\documentclass[modern]{aastex61}
\usepackage{xspace}
\newcommand{\escapecmd}[1]{\texttt{\detokenize{#1}}}

@@

Robust statistics provide reliable estimates of basic statistics for complex distributions that largely mitigate the effects of outliers. The \package{stats} package includes several robust statistical functions that are commonly used in astronomy. This includes sigma clipping methods to rejecting outliers, median absolute deviation functions, and biweight estimators, which have been used to calculate the velocity dispersion of galaxy clusters \citep{Beers1990}.

@@

>>>>

\documentclass[modern]{aastex61}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{booktabs}
\newcommand{\escapecmd}[1]{\texttt{\detokenize{#1}}}

@@

Robust statistics provide reliable estimates of basic statistics for complex distributions that largely mitigate the effects of outliers. The \package{stats} package includes several robust statistical functions that are commonly used in astronomy. This includes sigma clipping methods for rejecting outliers, median absolute deviation functions, and biweight estimators, which have been used to calculate the velocity dispersion of galaxy clusters \citep{Beers1990}.

@@

\begin{table}[h]
  \centering
  \caption{Registry of affiliated packages.}
  \label{tab:registry}
  \begin{tabular}{cccc}
    \toprule
    Package Name  & Stable & PyPI Name & Maintainer \\
    \midrule
      \input{registry.tex}
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}[h]
  \centering
  \caption{Registry of provisionally accepted affiliated packages.}
  \label{tab:registry_prov}
  \begin{tabular}{cccc}
    \toprule
    Package Name  & Stable & PyPI Name & Maintainer \\
    \midrule
      \input{registry_prov.tex}
    \bottomrule
  \end{tabular}
\end{table}
